---
title: "F.I.V.E. -- Developing a framework using a package structure"
author: "Lucio Rezende Queiroz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

# five

```{r setup}
knitr::opts_knit$set(root.dir = '~/projects/five/' )
#knitr::opts_chunk$set(comment=NA, fig.width=6, fig.height=6)
```

# Setting options

```{r, eval=FALSE}
getOption("devtools")
getOption("devtools.path")
getOption("devtools.name")
getOption("devtools.desc.author")
getOption("devtools.desc.license")

options(
  devtools.name = "Lucio Rezende Queiroz",
  devtools.desc.author = 
    'person(
      "Lucio", "Rezende Queiroz",
      email = "luciorqueiroz@gmail.com",
      role = c("aut", "cre"),
      comment = c(ORCID="0000-0002-6090-1834")
    )'
  )

options(
  usethis.name = "Lucio Rezende Queiroz",
  usethis.full_name = "Lucio Rezende Queiroz",
  usethis.description = list(
      `Authors@R` = 'person(
                      "Lucio", "Rezende Queiroz", 
                      email = "luciorqueiroz@gmail.com",
                      role = c("aut", "cre"),
                      comment = c(ORCID="0000-0002-6090-1834")
                    )',
    License = "MIT + file LICENSE",
    Version = "0.1.0"
  )
)
getOption("usethis.description")
```

# creating package

```{r, eval=FALSE}
usethis::create_package(here::here("projects","five"))
```
# Change project build information

Menu: Build > Configure Build Tools > check:
* Generate Documentation with roxygen and all suboptions in `configure`

Add check parameter `--as-cran` (Check Parameter - R CMD check)

# Setting dependencies

```{r}
cran_packages_to_use <- c(
  "dplyr",
  "ggplot2",
  "readr",
  "reshape",
  "plyr",
  "gplots",
  "scales",
  "RColorBrewer",
  "stringr",
  "fs",
  "here",
  "ggrepel",
  "optparse"
)
## Bioconductor packages
bioc_packages_to_use <- c()
packages_to_use <- c(cran_packages_to_use, bioc_packages_to_use)
## Add to description file Imports field
output <- purrr::map(
  packages_to_use,
  usethis::use_package
)
```

If you are using [Bioconductor](https://www.bioconductor.org/) packages dependencies you
need to add the following line to description file, before `Imports:` field:

```{}
biocViews:

```

## Suggested packages, used in tests and vignettes

```{r, eval=FALSE}
## 
usethis::use_package("lintr", type = "Suggests")

```


# Setting package infrastucture

```{r, eval=FALSE}
#usethis::use_usethis()
#usethis::use_rstudio()
usethis::use_readme_rmd()
usethis::use_mit_license()
usethis::use_code_of_conduct()
usethis::use_git()
usethis::use_git_config()
usethis::use_github(protocol = "https")
usethis::use_news_md()

```

